The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-01-26 src/ms.tex
Include community-orientated infrastructure section

Infrastructure packages that exist to support and help others maintain their
package infrastructure.

This includes an overview of the sphinx-astropy tools, the pytest extensions
maintained by astropy, and the package template.

@@

The Astropy Roadmap is a document in the astropy-project repository that captures high level actionable items that the Astropy project aims to undertake to improve the health and stability of the  project. It is a static document that is revisited regularly at the Astropy coordination meetings, to keep track of progress and write new versions as needed. There is a related project board linked to the Roadmap document, that holds specific issues and efforts related to Roadmap items. The project board is a living document that is continually updated as work is planned, assigned, and completed.

All items in the Roadmap have been agreed to be priorities for the Astropy Project, and are color-coded based on resources (both time/effort and developers/expertise) needed to complete the item. Green items are well underway, have sufficient resources/support and a plan in place for completion. Orange items are well defined, and work for aquiring sufficient resources underway. Red items do not yet have a plan for implementation and need more resources.

The Astropy Roadmap originates from the March 2021 Astropy Coordination meeting where it was first drafted before being handed off to a newly formed Astropy Roadmap working group for completion. The Roadmap in its currant form was adopted via pull request in December 2021.

>>>>

The Astropy project supports the broader ecosystem by providing pre-configured 
infrastructure packages that the community can use to support and maintain 
their own software package infrastructure. These include tools to easily 
generate documentation and setup automated testing, as well as provide 
package scaffolding for new projects.

Sphinx is a common and useful tool for generating documentation for Python 
packages. The Astropy project maintains a default Sphinx configuration along 
with Astropy-specific extensions which can be easily added to community 
projects via the \texttt{sphinx-astropy} meta package. This tool provides 
a pre-configured Sphinx setup compatible with Astropy projects, which 
includes several extensions useful for generating API documentation 
(\texttt{sphinx-automodapi}), allowing for Numpy docstring parsing 
(\texttt{numpydoc}), embedded image handling (\texttt{sphinx-gallery}; 
\texttt{pillow}), advanced documentation testing support 
(\texttt{pytest-doctestplus}), and providing a custom documentation theme 
ideal for analysis packages (\texttt{astropy-sphinx-theme}).

Community package testing infrastructure is supported through the 
\texttt{pytest-astropy} meta-package, providing a unified testing framework 
with useful extensions compatible with both Astropy- and 
non-Astropy-affiliated community packages. This meta-package pulls in several 
\texttt{pytest} plugins to help with custom test headers 
(\texttt{pytest-astropy-header}), accessing remotely-hosted data files in 
tests (\texttt{pytest-remotedata}), interoperability with documentation 
(\texttt{pytest-doctestplus}), dangling file handle checking 
(\texttt{pytest-openfiles}), data array comparison support in tests 
(\texttt{pytest-arraydiff}), sub-package command-line testing support 
(\texttt{pytest-filter-subpackage}), improved mock object testing 
(\texttt{pytest-mock}), test coverage reports and measurements 
(\texttt{pytest-cov}), and configuring package for property-based 
testing (\texttt{hypothesis}).

The Astropy Package Template helps facilitate the setup and creation of new 
Python packages leveraging the Astropy ecosystem. This tool utilizes the 
Cookiecutter project to walk users through the process of creating new 
packages complete with documentation and testing support. Additionally, the 
package template generation process includes the ability to setup 
interoperability with GitHub, allowing for easy repository access from 
documentation, as well as an example GitHub Actions workflow to demonstrate 
the use of GitHub's continuous integration tooling.

@@

Overview of roadmap and some highlights.
